%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, top=0.5in, bottom=0.5in, left=0.6in, right=0.6in}
\setlength\parindent{0in}
\pagestyle{empty}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}

\usepackage[bookmarks, colorlinks, breaklinks,
  pdftitle={Lorenzo Masoero - Resume},
  pdfauthor={Lorenzo Masoero},
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\begin{document}
\newcommand{\mm}{\textbf{M}.}

\begin{center}
{\LARGE\bfseries Lorenzo Masoero}\\[2pt]
\href{mailto:lo.masoero@gmail.com}{lo.masoero@gmail.com} \quad$\cdot$\quad \href{http://lorenzomasoero.com}{lorenzomasoero.com} \quad$\cdot$\quad \href{https://scholar.google.com/citations?user=qFFGfdYAAAAJ}{Google Scholar}
\end{center}

\section{Summary}

Senior Applied Scientist at Amazon Weblab (Amazon's largest A/B testing platform). Research focus on causal inference, experimental design, and agentic AI for experimentation---with publications in JRSS-B, Statistical Science, NeurIPS, Biometrika, and JASA. PhD from MIT (EECS), supervised by Prof.\ Tamara Broderick.

\section{Experience}

\textbf{Senior Applied Scientist III} \hfill Amazon, Weblab \quad 2021--Present\\[2pt]
\textbf{Online Experimentation with Interference.} Pioneered ``multiple randomization designs'' (joint work with Prof.\ Guido Imbens and Prof.\ Thomas Richardson, amongst others)---experiments that jointly randomize across multiple marketplace units to detect spillover effects. Published in \href{https://doi.org/10.1093/jrsssb/qkaf073}{\color{blue}{JRSS-B}} (2026) and \href{https://projecteuclid.org/journals/statistical-science/advance-publication/Experimental-Design-in-Marketplaces/10.1214/23-STS883.short}{\color{blue}{Statistical Science}} (2023).\\[3pt]
\textbf{Advancing Experimentation Methodology.} Deployed a distributed PySpark engine for \href{https://proceedings.mlr.press/v218/masoero23a.html}{\color{blue}{covariate-adjusted causal estimation}} (KDD 2023) serving thousands of daily experiments. Developed \href{https://arxiv.org/abs/2603.06941}{\color{blue}{Demonstration Experiments}} (with Vijaykumar \& Imbens) and \href{https://arxiv.org/abs/2506.12654}{\color{blue}{robust switchback designs}} (with Missault) for time-randomized experiments.\\[3pt]
\textbf{Agentic Workflows for Experimentation.} Built a multi-agent system for automated documentation maintenance (TriAgent, EMNLP 2026 submission) and autonomous LLM experimenters for A/B test analysis (AMLC 2026 Workshop).

\section{Education}

\textbf{PhD, Electrical Engineering and Computer Science} \hfill MIT, 2016--2021\\
Advisor: Prof.\ Tamara Broderick. Thesis on Bayesian nonparametric methods for genomic variant discovery.\\[2pt]
\textbf{MA, Statistics and Applied Mathematics} (with distinction) \hfill Collegio Carlo Alberto, 2015--2016\\[2pt]
\textbf{MA, Quantitative Finance} (110/110 magna cum laude) \hfill Universit\`{a} di Torino, 2015--2016\\[2pt]
\textbf{BA, Economics} (110/110 cum laude) \hfill Universit\`{a} di Torino, 2012--2014

\section{Selected Publications}

\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
\item \href{https://doi.org/10.1093/jrsssb/qkaf073}{Multiple Randomization Designs: Estimation and Inference with Interference.} JRSS-B, 2026.
\item \href{https://arxiv.org/abs/2405.18621}{Multi-Armed Bandits with Network Interference.} NeurIPS 2024.
\item \href{https://projecteuclid.org/journals/statistical-science/advance-publication/Experimental-Design-in-Marketplaces/10.1214/23-STS883.short}{Experimental Design in Marketplaces.} Statistical Science, 2023.
\item \href{https://academic.oup.com/biomet/advance-article-abstract/doi/10.1093/biomet/asab012/6146908}{More for Less: Predicting and maximizing genetic variant discovery via BNP.} Biometrika, 2022.
\item \href{https://www.tandfonline.com/doi/full/10.1080/01621459.2022.2115918}{Scaled process priors for new-feature counts via random scaling in BNP.} JASA, 2022.
\item \href{https://arxiv.org/abs/2603.06941}{Demonstration Experiments.} Pre-print, 2025.
\item From Offline Evidence to Online Action. ICML 2026 Workshop.
\end{itemize}

\section{Awards}

\textbf{SBSS Best Student Paper Award}, American Statistical Association (2020) \quad$\cdot$\quad Andrew \& Erma Viterbi Fellowship (2017)

\section{Service}

Reviewer for JRSS-B, JASA, JMLR, NeurIPS, KDD, AISTATS, ProbML (2018--2026).

\section{Skills}

Python (NumPy, SciPy, Pandas, PySpark, scikit-learn) \quad$\cdot$\quad Bayesian inference \& causal inference \quad$\cdot$\quad \LaTeX

\end{document}
