\section*{Research}
%\years{2020} 
\begin{itemize}
	\item ``\href{https://arxiv.org/abs/2603.19480}{{\textbf{Regression Adjustments for Double Randomization in Two-Sided Marketplaces}}''} (pre-print; Sudijono, Lei, \mm, Vijaykumar, Imbens, McQueen). Manuscript available at \href{https://arxiv.org/abs/2603.19480}{\textcolor{blue}{arXiv:2603.19480}}
	\item ``\href{https://arxiv.org/abs/2603.06941}{{\textbf{Demonstration Experiments}}''} (pre-print; Imbens, \mm, Rakhlin, Richardson, Vijaykumar). Manuscript available at \href{https://arxiv.org/abs/2603.06941}{\textcolor{blue}{arXiv:2603.06941}}
	\item ``\textbf{Carryover detection in switchback experimentation}''; CauScien Workshop, NeurIPS 2025. (\href{https://openreview.net/pdf?id=fyfkP1TOKW}{Missault, \mm}); Manuscript available at \href{https://openreview.net/pdf?id=fyfkP1TOKW}{\textcolor{blue}{openreview}}
	\item ``\textbf{Optimizing duration of online experiments via Bayesian early termination}''; \textcolor{red}{Spotlight talk} at Code@MIT 2025. (\mm, Gualavisi); Manuscript available at \href{https://www.amazon.science/publications/optimizing-duration-of-online-experiments-via-bayesian-early-termination}{\textcolor{blue}{Amazon Science}}
	\item ``\textbf{Rethinking Power in Online Experimentation: Connecting Frequentist and Bayesian Approaches to Inform Experiment Design}''; \textcolor{red}{Spotlight talk} at Code@MIT 2025. (Gualavisi, Kessler, \mm). Manuscript available at \href{https://www.amazon.science/publications/statistical-power-calculations-revisited-incorporating-beliefs-about-effect-sizes}{\textcolor{blue}{Amazon Science}}
	\item ``\href{https://arxiv.org/abs/2506.12654}{{\textbf{Robust and efficient multiple-unit switchback experimentation}}''} Code@MIT 2025. (Missault, \mm, Delb\'{e}, Richardson, Imbens). Manuscript available at \href{https://www.amazon.science/publications/regular-balanced-switchback-designs-for-robust-multi-unit-online-experimentation}{\textcolor{blue}{Amazon Science}}. Working paper available at \href{https://arxiv.org/html/2506.12654}{\textcolor{blue}{arXiv:2506.12654}}
	\item ``\href{https://arxiv.org/abs/2505.19643}{{\textbf{Online activity prediction via generalized Indian buffet process models}}''} (pre-print; Beraha, \mm, Favaro, Richardson). Manuscript available at \href{https://arxiv.org/abs/2505.1964}{\textcolor{blue}{arXiv:2505.1964}}
	\item ``\href{https://drive.google.com/drive/folders/1557KDfzlwEi-Pn3J0fDgMX3XWwSqyeij}{{\textbf{Measuring direct and Indirect Impacts in a Multi-Sided Marketplace: Evidence from a Clustered Multiple Randomization Experiment}}''} CODE@MIT2024, KDD 2024, Workshop on Two-Sided Marketplace Optimization; (Hut, Imbens, \mm, Vijaykumar). Manuscript available at \href{https://drive.google.com/drive/folders/1557KDfzlwEi-Pn3J0fDgMX3XWwSqyeij}{\textcolor{blue}{Code@MIT 2024 proceedings}}
	\item ``\textbf{Multi-Armed Bandits with Network Interference}''; \href{https://arxiv.org/abs/2405.18621}{NeurIPS 2024}. (Agarwal, Agarwal, \mm, Whitehouse). Manuscript available at \href{https://arxiv.org/abs/2405.18621}{\textcolor{blue}{arXiv}}
	\item ``\textbf{Double trouble: Predicting new variant counts across two heterogeneous populations}''; \href{https://arxiv.org/pdf/2403.02154.pdf}{arXiv preprint, 2403.02154}. (Shen, \mm, Schraiber, Broderick). Bayesian Analysis, 2026+; Manuscript available at \href{https://arxiv.org/pdf/2403.02154.pdf}{\textcolor{blue}{arXiv}}; earlier version accepted at \href{https://www.lmrl.org/}{Learning Meaningful Representations of Life},  Neural Information Processing Systems Workshop, 2022. (Shen, \mm, Schraiber, Broderick) (manuscript available at \href{https://openreview.net/pdf?id=euBgC9yLeyl}{\textcolor{blue}{OpenReview}})
	\item ``\textbf{Improved prediction of future user activity in online A/B testing}''; \href{https://arxiv.org/abs/2402.03231}{arXiv preprint, 2402.03231}. (\mm, Beraha, Richardson, Favaro). Manuscript available at \href{https://arxiv.org/abs/2402.03231}{\textcolor{blue}{arXiv}}
	\item ``\textbf{A Nonparametric Bayes Approach to Online Activity Prediction}''; \href{https://arxiv.org/abs/2401.14722}{arXiv preprint, 2401.14722}. (Beraha, \mm, Richardson, Favaro). Manuscript available at \href{https://arxiv.org/abs/2401.14722}{\textcolor{blue}{arXiv}}
	\item ``\textbf{Multiple Randomization Designs: Estimation and Inference with Interference.}'' \href{https://arxiv.org/abs/2401.01264}{arXiv preprint, 2401.01264.} (\mm, Vijaykumar, Richardson, McQueen, Rosen, Burdick, Bajari, Imbens). Manuscript available at \href{https://arxiv.org/abs/2401.01264}{\textcolor{blue}{arXiv}}
	\item ``\textbf{Leveraging covariate adjustments at scale in online A/B testing}''; \href{https://proceedings.mlr.press/v218/masoero23a.html}{2023 KDD Workshop on Causal Discovery, Prediction and Decision, PMLR 218:25-48, 2023.} (\mm, McQueen, Hains). Manuscript available at \href{https://proceedings.mlr.press/v218/masoero23a.html}{\textcolor{blue}{PMLR}}
	\item ``\textbf{Experimental Design in Marketplaces}''; \href{https://projecteuclid.org/journals/statistical-science/advance-publication/Experimental-Design-in-Marketplaces/10.1214/23-STS883.short}{Statistical Science, 38(3): 458-476 (August 2023)}. (Bajari, Burdick, Imbens, \mm, McQueen, Richardson, Rosen). Manuscript available at \href{https://www.amazon.science/publications/experimental-design-in-marketplaces}{\textcolor{blue}{Amazon Science}}.
	\item ``\textbf{Independent Finite Approximations for Bayesian Nonparametric Inference}''; Bayesian Analysis, Advance Publication 1-38 (2023). (Nguyen, Huggins, \mm, Mackey, Broderick). Manuscript available at \href{https://arxiv.org/pdf/2009.10780.pdf}{\textcolor{blue}{arXiv}}
	\item``\textbf{Cross-Study Replicability in Cluster Analysis}''. Statistcal Science, 38(2): 303-316 (May 2023).  (\mm, Thomas, Parmigiani, Tyekucheva, Trippa). Manuscript available at \href{https://arxiv.org/pdf/2202.01910.pdf}{\textcolor{blue}{arXiv}}
	\item ``\textbf{Multiple Randomization Designs}''; (Bajari, Burdick, Imbens, \mm, McQueen, Richardson, Rosen). Manuscript available at \href{https://arxiv.org/pdf/2112.13495.pdf}{\textcolor{blue}{arXiv}}
	\item ``\textbf{Bayesian nonparametric strategies for power maximization in rare variants association studies}''; \textcolor{red}{\textbf{Spotlight}} at \href{https://www.lmrl.org/}{Learning Meaningful Representations of Life},  Neural Information Processing Systems, 2021 [\href{https://lorenzomasoero.com/files/LRML_21_poster.pdf}{\textcolor{blue}{poster}}]. (\mm, Schraiber, Broderick). Manuscript available at \href{https://arxiv.org/pdf/2112.02032.pdf}{\textcolor{blue}{arXiv}}
	\item ``\textbf{The Chicago Police Department dataset}''; Neural Information Processing Systems Track on Datasets and Benchmarks, 2021, \href{https://github.com/chicago-police-violence/data}{\textcolor{blue}{Dataset repository}}, \href{https://github.com/chicago-police-violence/data/releases/tag/v0.1}{\textcolor{blue}{current release (v0.1)}} and \href{https://github.com/chicago-police-violence/data/releases/download/v0.1/documentation.pdf}{\textcolor{blue}{documentation}} (Horel, \mm, Agrawal, Roithmayr, Campbell)
	\item ``\textbf{Scaled process priors: Improved predictions and uncertainties for new-feature counts via random scaling in Bayesian nonparametrics}''; Accepted for publication in the \href{https://www.tandfonline.com/doi/full/10.1080/01621459.2022.2115918}{Journal of the American Statistical Association}. (Camerlenghi, Favaro, \mm and T. Broderick). Manuscript available at \href{https://arxiv.org/pdf/2106.15480.pdf}{\textcolor{blue}{arXiv}} [\href{https://lorenzomasoero.com/files/spp_poster.pdf}{\textcolor{blue}{poster}}]. Featured in \href{https://whova.com/portal/webapp/isbaw_202106/}{ISBA 2021}
	\item ``\textbf{More for Less: Predicting and maximizing genetic variant discovery via Bayesian nonparametrics}''; to appear in \href{https://academic.oup.com/biomet/advance-article-abstract/doi/10.1093/biomet/asab012/6146908?redirectedFrom=PDF}{Biometrika}.  \href{https://community.amstat.org/sbss/home}{\textbf{\textcolor{red}{Best Student Paper Award}}, awarded by the American Statistical Association, Section in Bayesian Statistical Science}. (\mm, Camerlenghi, Favaro, Broderick). Manuscript available at \href{https://arxiv.org/pdf/1912.05516.pdf}{\textcolor{blue}{arXiv}} \href{https://lorenzomasoero.com/files/more_poster.pdf}{\texttt{[\textcolor{blue}{poster}; \href{https://www.youtube.com/watch?v=OQzyWf-OXK4&ab_channel=TamaraBroderick}{\textcolor{blue}{presentation (YouTube)}}]}}. Featured in \href{https://liphlab.github.io/SMEEB2021/files/SMEEB2021_abstract_booklet.pdf}{SMEEB 2021}, \href{https://www.ashg.org/meetings/2020meeting}{ASHG 2020},  \href{https://openreview.net/pdf?id=B1l8tyhEYr}{AABI 2019}
	\item``\textbf{Posterior representations of hierarchical completely random measures in trait allocation models}'', \href{https://sites.google.com/view/nipsbnp2018/accepted-papers}{\textcolor{red}{\textbf{Spotlight}}, \emph{BNP@NeurIPS2018}} \href{https://lorenzomasoero.com/files/bnp_neurips_2018_poster.pdf}{\texttt{[\textcolor{blue}{poster}]}}  (\mm, Camerlenghi, Favaro and Broderick)
 	\item ``\textbf{Sensitivity of Bayesian inference to data perturbations}'', \href{http://approximateinference.org/accepted/}{\emph{AABI 2018}} \href{https://lorenzomasoero.com/files/aabi_2018_poster.pdf}{\texttt{[\textcolor{blue}{poster}]}} (\mm, Stephenson, Broderick)
\item \href{http://www.approximateinference.org/2017/accepted/HugginsEtAl2017.pdf}{``\textbf{Generic finite approximations
for practical Bayesian nonparametrics}'', \textcolor{red}{\textbf{Spotlight}}, \emph{NIPS 2017 Workshop on Advances in Approximate Bayesian Inference}} \href{https://lorenzomasoero.com/files/aabi_2017_poster.pdf}{\texttt{[\textcolor{blue}{poster}]}}.  (Huggins, \mm, Mackey, Broderick). Manuscript available at \href{http://www.approximateinference.org/2017/accepted/HugginsEtAl2017.pdf}{\textcolor{blue}{NIPS Workshop}}
\end{itemize}
